Title of My Article\titlelinebreak{} with a Forced Linebreak

### 2013-06-27 mt-marathon.2012/PBML_article.tex
from google doc

\institute{label1}{IBM}
\institute{label2}{CNGL, Dublin City University}
\institute{label3}{Center for Language and Speech Processing, Johns Hopkins University}
\institute{label4}{Carnegie Mellon University}

\author{
  firstname=Humpty,
  surname=Dumpty,
  institute=label1,
}
\author{
  firstname=Mock,
  surname=Turtle,
  institute={label2,label4},
  corresponding=yes,
  email={turtle@seacoast.wl},
  address={Carnegie Mellon University\\407 S. Craig Street, Pittsburgh, PA 15213, United States}
}
\author{
  firstname=Cheshire,
  initials=C.,
  surname=Cat,
  institute=label3,
}

>>>>

\institute{label1}{University of Edinburgh}
\institute{label2}{Center for Language and Speech Processing, Johns Hopkins University}
\institute{label3}{Carnegie Mellon University}

\author{
  firstname=Hieu,
  surname=Hoang,
  institute=label1,
}
\author{
  firstname=Matt,
  surname=Post,
  institute=label2,
}
\author{
  firstname=Chris,
  surname=Dyer,
  institute=label3,
}
\author{
  firstname=Eva,
  surname=Hasler,
  institute=label1,
}
\author{
  firstname=Barry,
  surname=Haddow,
  institute=label1,
}
\author{
  firstname=Philipp,
  surname=Koehn,
  institute=label1,
}
